\section[A discussion of the differences between the video shot detection methods, and the influence of these differences on 1) the precision and recall values and 2) the computational complexity]{}

As shown in Figure \ref{grafiek} in Appendix \ref{app:q6}, the pixel method, while being very simple, achieves quite reasonable results when calibrated right. The second method is the motion method, whose results are better since it gets less confused by motion. However, the results are far from perfect. In an experimental attempt to optimize this method, an auto mode was implemented. This auto mode keeps track of the average of the difference between frames and reports a shot when the current difference exceeds a multiple of the average. This method is among the best ones, but is slow due to the complex motion estimation. This problem is easily solved using a speedup, a speedup of 4 means that the motion algorithm only processes 1 in 4 blocks. These speedups are useful for high resolution sequences.

Next up are the histogram methods, where the local histogram scores a lot better than the global histogram, due to its ability to detect more fades and more difference in the frame (because it checks for local differences). For instance, if only the camera angle changes between shots, then the average color values will still be more or less the same, but the colors will appear at different places. The local method does detect this by checking averages per region instead of one global average. The added complexity for the local histogram method is thus justified with higher results.

The winner for the star wars method for precision and recall is the twin comparison, which has the highest precision (94\%) and recall (92\%), while also being the fastest method. This is no surprise, since the twin comparison is the most complex method. Given its score, the added complexity is certainly justified here. Even though the results are high, they are not perfect, this is because twin comparison does a bad job at detecting dissolves.
\\